TCP Congestion Algorithms In Datacenters \\ \vspace{0.3cm} {\large LS Project}

### 2017-11-23 paper/paper.tex
Written part of Methods

\section{Method}

>>>>

\section{Method}
During this research a performance test of various TCP congestion algorithms will be performed. The TCP congestion algorithms will be determined through desk research of the most common algorithms. The tests will be conducted in a private environment. Based on the results of those tests, recommendations will be given related to the measures a datacenter has to take to keep the traffic equally allocated over customers.

	\subsection{Comparing Performance}
	Two scenarios will be used to compare the performance of the TCP 				congestion algorithms:
	\begin{enumerate}
		\item The user owns one endpoint in the network. In this case only 				the sender side has a congestion algorithm applied.
		\item The user owns multiple endpoints in the network. In this case a			congestion algorithm is applied at both the client and server side.
	\end{enumerate}

	The created environments are shown in figure ... and figure ...
